### 2015-05-15 intro.tex
fix

We present \whoop, an automated approach for static data race analysis in device drivers. \whoop is empowered by \emph{symbolic pairwise lockset analysis}, which attempts to prove a driver race-free by: (i) deriving a sound \emph{sequential} program that \emph{over-approximates} the originally concurrent program; (ii) instrumenting it to record \emph{locksets}; and (iii) using the locksets to assert that all accesses to the same shared resource are consistently protected by a common lock. Reducing analysis to reasoning over a sequential program avoids the need to enumerate thread interleavings, and allows reuse of existing successful sequential verification techniques.
%
We show that we can exploit the race-freedom guarantees provided by our symbolic analysis to achieve a sound partial-order reduction that significantly accelerates \corral~\cite{lal2012corral}, a precise bug-finder used by Microsoft to analyze drivers and other concurrent programs. Using \whoop and \corral we analyzed \sizeOfBenchmarks drivers from the 4.0 Linux kernel distribution.  By combining \whoop and \corral we achieve analysis speedups in the range of 1.5--10$\times$ for most of our benchmarks, compared with using \corral in isolation.  For two drivers, we observed even greater speedups of 12$\times$ and 20$\times$.
%
\whoop currently supports Linux drivers, but our approach is conceptually generic and could be applied to analyze drivers for other operating systems, as well as to concurrent systems that use a similar programming model (e.g.\ file systems).

>>>>

We present \whoop, an automated approach for static data race analysis in device drivers. \whoop is empowered by \emph{symbolic pairwise lockset analysis}, which attempts to prove a driver race-free by: (i) deriving a sound \emph{sequential} program that \emph{over-approximates} the originally concurrent program; (ii) instrumenting it to record \emph{locksets}; and (iii) using the locksets to assert that all accesses to the same shared resource are consistently protected by a common lock. Reducing analysis to reasoning over a sequential program avoids the need to enumerate thread interleavings, and allows reuse of existing successful sequential verification techniques.
%
We show that we can exploit the race-freedom guarantees provided by our symbolic analysis to achieve a sound partial-order reduction that significantly accelerates \corral~\cite{lal2012corral}, a precise bug-finder used by Microsoft to analyze drivers and other concurrent programs. Using \whoop and \corral we analyzed \sizeOfBenchmarks drivers from the 4.0 Linux kernel distribution.  By combining \whoop and \corral we achieve analysis speedups in the range of 1.5--10$\times$ for most of our benchmarks, compared with using \corral in isolation.  For two drivers, we observed even greater speedups of 12$\times$ and 20$\times$.
%
\whoop currently supports Linux drivers, but our approach is conceptually generic and could be applied to analyze drivers for other operating systems as well as concurrent systems that use a similar programming model (e.g.\ file systems).
